### 2017-05-11 Publications/Original Software Publications/Science of Computer Programming/comments/comments.tex
updating comments
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

\begin{itemize}
\item Page 2
  \begin{itemize}
  \item \sout{space-state exploration $\rightarrow$ state-space exploration;}
  \item \sout{ESBMC-GPU builds on top of ESBMC $\rightarrow$ ESBMC-GPU is built on top of ESBMC;}
  \end{itemize}
\item Page 3
  \begin{itemize}
  \item consists in $\rightarrow$ consists of;
  \item Besides, in: remove ``Besides'';
  \item reduce state space $\rightarrow$ reduce the state space;
  \end{itemize}
\item Page 4
  \begin{itemize}
  \item if multiple threads perform unsynchronized 90 access to shared-memory locations: to the same memory locations, it is crucial to mention that;
  \item has been systematically explored $\rightarrow$ have been systematically explored;
  \item Therefore: the next conclusion does not follow logically from the previous statements, so ``therefore'' should be removed here;
  \end{itemize}
\item Page 5
  \begin{itemize}
  \item Figure 2: between lines 17 and 18, the contents of {\tt dev\_a} should be copied to a with a {\tt cudaMemcpy}, otherwise the subsequent check is quite useless;
  \end{itemize}
\item Page 6
  \begin{itemize}
  \item In addition $\rightarrow$ On the other hand;
  \item Besides, it further simplifies verification models: further compared to what? How does it make it easier?
  \item if compared: remove ``if'';
  \item stream interleaving: what is this?
  \item  to reduce the number of thread interleavings: in what respect? Not reducing the number of threads, right? You already use the 2-thread simplification;
  \end{itemize}
\end{itemize}

>>>>

\begin{itemize}
\item \sout{Page 2}
  \begin{itemize}
  \item \sout{space-state exploration $\rightarrow$ state-space exploration;}
  \item \sout{ESBMC-GPU builds on top of ESBMC $\rightarrow$ ESBMC-GPU is built on top of ESBMC;}
  \end{itemize}
\item \sout{Page 3}
  \begin{itemize}
  \item \sout{consists in $\rightarrow$ consists of};
  \item \sout{Besides, in: remove ``Besides'';}
  \item \sout{reduce state space $\rightarrow$ reduce the state space;}
  \end{itemize}
\item Page 4
  \begin{itemize}
  \item if multiple threads perform unsynchronized 90 access to shared-memory locations: to the same memory locations, it is crucial to mention that;
  \item \sout{has been systematically explored $\rightarrow$ have been systematically explored;}
  \item \sout{Therefore: the next conclusion does not follow logically from the previous statements, so ``therefore'' should be removed here;}
  \end{itemize}
\item Page 5
  \begin{itemize}
  \item Figure 2: between lines 17 and 18, the contents of {\tt dev\_a} should be copied to {\tt a} with a {\tt cudaMemcpy}, otherwise the subsequent check is quite useless;
  \end{itemize}
\item Page 6
  \begin{itemize}
  \item In addition $\rightarrow$ On the other hand;
  \item Besides, it further simplifies verification models: further compared to what? How does it make it easier?
  \item if compared: remove ``if'';
  \item stream interleaving: what is this?
  \item  to reduce the number of thread interleavings: in what respect? Not reducing the number of threads, right? You already use the 2-thread simplification;
  \end{itemize}
\end{itemize}
